Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-02-07 paper/main.tex
Updates

\begin{figure}[t!]
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=1]{example.pdf}
		\caption{True DAG}
	\end{subfigure}%
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=2]{example.pdf}
		\caption{No edges.}
	\end{subfigure}%
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=3]{example.pdf}
		\caption{Orient $ X_1 \rightarrow X_4 $}
	\end{subfigure}
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=4]{example.pdf}
		\caption{Orient $ X_1 \rightarrow X_2 $}
	\end{subfigure}%
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=5]{example.pdf}
		\caption{Orient $ X_1 \rightarrow X_3 $}
	\end{subfigure}%
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=6]{example.pdf}
		\caption{Orient $ X_2 \rightarrow X_4 $}
	\end{subfigure}
	\begin{subfigure}{0.17 \textwidth}
		\includegraphics[page=7]{example.pdf}
		\caption{Expand $ X_3 \rightarrow X_4 $. Prune $ X_1 \rightarrow X_4 $.}
	\end{subfigure}
	\caption{An example showing the steps of \textit{ExpertInLoop} algorithm. The dashed edges show all the potential edges that \textit{Expand} algorithm could add in each step.
	}
\end{figure}

@@

We analyzed the performance of this manual approach by comparing it with two
automated algorithms: PC and Greedy Equivalence Search (GES). For the
comparison we use simulated data from a known DAG and compare how well the
algorithm is able to recover the original model using two metrics: Structural
Hamming Distance (SHD) and Structural Intervention Distance (SID). To simulate
the data, we start with a randomly generated DAG on $ 10 $ nodes and use linear
models with random effects to generate the data.

>>>>

\begin{figure}[t!]
	\begin{subfigure}{0.125 \textwidth}
		\centering
		\includegraphics[page=1]{example.pdf}
		\caption{True DAG}
	\end{subfigure}%
	\begin{subfigure}{0.125 \textwidth}
		\centering
		\includegraphics[page=2]{example.pdf}
		\caption{No edges.}
	\end{subfigure}%
	\begin{subfigure}{0.125 \textwidth}
		\centering
		\includegraphics[page=3]{example.pdf}
		\caption{$ X_1 \rightarrow X_4 $}
	\end{subfigure}%
	\begin{subfigure}{0.125 \textwidth}
		\centering
		\includegraphics[page=4]{example.pdf}
		\caption{$ X_1 \rightarrow X_2 $}
	\end{subfigure}
	\begin{subfigure}{0.125 \textwidth}
		\centering
		\includegraphics[page=5]{example.pdf}
		\caption{$ X_1 \rightarrow X_3 $}
	\end{subfigure}%
	\begin{subfigure}{0.125 \textwidth}
		\centering
		\includegraphics[page=6]{example.pdf}
		\caption{$ X_2 \rightarrow X_4 $}
	\end{subfigure}%
	\begin{subfigure}{0.250 \textwidth}
		\centering
		\includegraphics[page=7]{example.pdf}
		\caption{$ X_3 \rightarrow X_4 $. $ X_1 \not \rightarrow X_4 $.}
	\end{subfigure}
	\caption{An example showing the steps of \textit{ExpertInLoop} algorithm. The dashed edges show all the potential edges that \textit{Expand} algorithm could add in each step.
	}
\end{figure}

@@

We analyzed the performance of \textit{ExpertInLoop} algorithm by comparing it
with three commonly used automated algorithms: PC, Hill-Climb Search, and
Greedy Equivalence Search (GES). For the analysis, we simulated data from known
DAG structures and

we use simulated data from
a known DAG and compare how well the algorithm is able to recover the original
model using two metrics: Structural Hamming Distance (SHD) and Structural
Intervention Distance (SID). To simulate the data, we start with a randomly
generated DAG on $ 10 $ nodes and use linear models with random effects to
generate the data.
